### 2022-11-11 dissertation/appendix/case-study-additional.tex
✨ (results): Recolored plots

\begin{figure}[htpb]
	\centering
	\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_HgEC/p_HgEC[0][1].pdf}
	\caption{The average unnormalised sampled posterior selection probability for heuristic $h_{1}$ (\acs{Momentum}), given the application to entity $e_{0}$ and requiring a successful credit allocation ($\gamma_{1}$) from the \textit{ibest} credit assignment strategy, sampled from the posterior selection probability distribution $P(h_{1} \vert \theta_{1} \vert e_{0}, \gamma_{1})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
	\label{fig:app:case_study_additional:p_HgEC:0:1}
\end{figure}

\begin{figure}[htpb]
	\centering
	\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_HgEC/p_HgEC[0][2].pdf}
	\caption{The average unnormalised sampled posterior selection probability for heuristic $h_{2}$ (\acs{NAG}), given the application to entity $e_{0}$ and requiring a successful credit allocation ($\gamma_{1}$) from the \textit{ibest} credit assignment strategy, sampled from the posterior selection probability distribution $P(h_{2} \vert \theta_{2} \vert e_{0}, \gamma_{1})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
	\label{fig:app:case_study_additional:p_HgEC:0:2}
\end{figure}

\begin{figure}[htpb]
	\centering
	\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_HgEC/p_HgEC[0][3].pdf}
	\caption{The average unnormalised sampled posterior selection probability for heuristic $h_{3}$ (\acs{Adagrad}), given the application to entity $e_{0}$ and requiring a successful credit allocation ($\gamma_{1}$) from the \textit{ibest} credit assignment strategy, sampled from the posterior selection probability distribution $P(h_{3} \vert \theta_{3} \vert e_{0}, \gamma_{1})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
	\label{fig:app:case_study_additional:p_HgEC:0:3}
\end{figure}

\begin{figure}[htpb]
	\centering
	\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_HgEC/p_HgEC[0][4].pdf}
	\caption{The average unnormalised sampled posterior selection probability for heuristic $h_{4}$ (\acs{RMSProp}), given the application to entity $e_{0}$ and requiring a successful credit allocation ($\gamma_{1}$) from the \textit{ibest} credit assignment strategy, sampled from the posterior selection probability distribution $P(h_{4} \vert \theta_{4} \vert e_{0}, \gamma_{1})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
	\label{fig:app:case_study_additional:p_HgEC:0:4}
\end{figure}

\begin{figure}[htpb]
	\centering
	\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_HgEC/p_HgEC[0][5].pdf}
	\caption{The average unnormalised sampled posterior selection probability for heuristic $h_{5}$ (\acs{Adadelta}), given the application to entity $e_{0}$ and requiring a successful credit allocation ($\gamma_{1}$) from the \textit{ibest} credit assignment strategy, sampled from the posterior selection probability distribution $P(h_{5} \vert \theta_{5} \vert e_{0}, \gamma_{1})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
	\label{fig:app:case_study_additional:p_HgEC:0:5}
\end{figure}

\begin{figure}[htpb]
	\centering
	\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_HgEC/p_HgEC[0][9].pdf}
	\caption{The average unnormalised sampled posterior selection probability for heuristic $h_{9}$ (\acs{DE}), given the application to entity $e_{0}$ and requiring a successful credit allocation ($\gamma_{1}$) from the \textit{ibest} credit assignment strategy, sampled from the posterior selection probability distribution $P(h_{9} \vert \theta_{9} \vert e_{0}, \gamma_{1})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
	\label{fig:app:case_study_additional:p_HgEC:0:9}
\end{figure}

>>>>

\begin{figure}[htpb]
	\centering
	\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_HgEC/p_HgEC[0][1].pdf}
	\caption{The average unnormalised sampled posterior selection probability for heuristic $h_{1}$ (\acs{Momentum}), given the application to entity $e_{0}$ and requiring a successful credit allocation ($\gamma_{1}$) from the \textit{ibest} credit assignment strategy, sampled from the posterior selection probability distribution $P(h_{1} \vert e_{0}, \gamma_{1})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
	\label{fig:app:case_study_additional:p_HgEC:0:1}
\end{figure}

\begin{figure}[htpb]
	\centering
	\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_HgEC/p_HgEC[0][2].pdf}
	\caption{The average unnormalised sampled posterior selection probability for heuristic $h_{2}$ (\acs{NAG}), given the application to entity $e_{0}$ and requiring a successful credit allocation ($\gamma_{1}$) from the \textit{ibest} credit assignment strategy, sampled from the posterior selection probability distribution $P(h_{2} \vert e_{0}, \gamma_{1})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
	\label{fig:app:case_study_additional:p_HgEC:0:2}
\end{figure}

\begin{figure}[htpb]
	\centering
	\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_HgEC/p_HgEC[0][3].pdf}
	\caption{The average unnormalised sampled posterior selection probability for heuristic $h_{3}$ (\acs{Adagrad}), given the application to entity $e_{0}$ and requiring a successful credit allocation ($\gamma_{1}$) from the \textit{ibest} credit assignment strategy, sampled from the posterior selection probability distribution $P(h_{3} \vert e_{0}, \gamma_{1})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
	\label{fig:app:case_study_additional:p_HgEC:0:3}
\end{figure}

\begin{figure}[htpb]
	\centering
	\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_HgEC/p_HgEC[0][4].pdf}
	\caption{The average unnormalised sampled posterior selection probability for heuristic $h_{4}$ (\acs{RMSProp}), given the application to entity $e_{0}$ and requiring a successful credit allocation ($\gamma_{1}$) from the \textit{ibest} credit assignment strategy, sampled from the posterior selection probability distribution $P(h_{4} \vert e_{0}, \gamma_{1})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
	\label{fig:app:case_study_additional:p_HgEC:0:4}
\end{figure}

\begin{figure}[htpb]
	\centering
	\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_HgEC/p_HgEC[0][5].pdf}
	\caption{The average unnormalised sampled posterior selection probability for heuristic $h_{5}$ (\acs{Adadelta}), given the application to entity $e_{0}$ and requiring a successful credit allocation ($\gamma_{1}$) from the \textit{ibest} credit assignment strategy, sampled from the posterior selection probability distribution $P(h_{5} \vert e_{0}, \gamma_{1})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
	\label{fig:app:case_study_additional:p_HgEC:0:5}
\end{figure}

\begin{figure}[htpb]
	\centering
	\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_HgEC/p_HgEC[0][9].pdf}
	\caption{The average unnormalised sampled posterior selection probability for heuristic $h_{9}$ (\acs{DE}), given the application to entity $e_{0}$ and requiring a successful credit allocation ($\gamma_{1}$) from the \textit{ibest} credit assignment strategy, sampled from the posterior selection probability distribution $P(h_{9} \vert e_{0}, \gamma_{1})$ over 250 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the Iris dataset, illustrated in log scale.}
	\label{fig:app:case_study_additional:p_HgEC:0:9}
\end{figure}
